Extending competitive accessibility for multi-modal analysis

### 2023-11-01 Response-to-reviewers_R1.Rmd

_Notably, plots in Figure \ref{fig:Fig4} can be observed across modes if curious to know what trips are more likely to occur using what mode depending on trip length (as informed by the observed 2018 survey). Trips >5 minutes do not occur frequently for any mode, as such trips with short trip lengths are assigned a lower travel impedance_ $f^m(c_{ij}^m)$ _value. One reason that >5 minute trips do not frequently occur as a result of land-use (residential and job mismatch): not everyone lives in immediate proximity to their workplace. In terms of the non-motorized modes, shorter trips occurred more frequently overall for walking populations, particularly around 15 minute lengths, so a trip of approximately 15 minutes is assigned the highest_ $f^m(c_{ij}^m)$. _For biking populations, longer travel times are more common so though the highest_ $f^m(c_{ij}^m)$ _value also corresponds to approximately 15 minutes, the curve is more spread out and values decrease less rapidly at longer travel times than for the walk mode curve. A similar trend can be observed for the motorized modal options where transit mode is more spread out than car/motor mode. All in all, these observations demonstrate that, based on a given mode and travel time, a trip is more or less likely to occur and is accordingly represented in the cost of travel balancing factor_ $F_{ij}^m$ _for_ $V_i^m$.
}

Minor issues:
1. As for Fig 2 and Fig 3, please indicate the meaning of the gray color blocks in illustration.
\textcolor{blue}{
Fixed for all Figures, thank you. }
2. Please change the color scheme of fig 2. The red color scheme makes the LEZ centro area boundary, which is also in red, not visible.
\textcolor{blue}{
WILL FIX THANK YOU <!-- and I must change the labels on the legends to be ranges -->}
